First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-08-30 eg6-letters/coherent/dvcs_he4_prl.tex
Progress on review answers

\bibitem{Berger:2001zb} 
  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
  %``Generalized parton distributions in the deuteron,''
  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
  [hep-ph/0106192].

\bibitem{Cano:2003ju} 
  F.~Cano and B.~Pire,
  %``Deep electroproduction of photons and mesons on the deuteron,''
  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
  [hep-ph/0307231].

\bibitem{Guzey:2005ba} 
  V.~Guzey and M.~Siddikov,
  %``On the A-dependence of nuclear generalized parton distributions,''
  J.\ Phys.\ G {\bf 32}, 251 (2006)
  [hep-ph/0509158].

@@

\bibitem{Guidal:2004nd}
M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 
Phys.\ Rev.\ D {\bf 72}, 054013 (2005).

>>>>

\bibitem{Berger:2001zb} 
  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
  [hep-ph/0106192].

\bibitem{Cano:2003ju} 
  F.~Cano and B.~Pire,
  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
  [hep-ph/0307231].

\bibitem{Guzey:2005ba} 
  V.~Guzey and M.~Siddikov,
  J.\ Phys.\ G {\bf 32}, 251 (2006)
  [hep-ph/0509158].

@@

\bibitem{Guidal:2004nd}
M.~Vanderhaeghen, P.A.M.~Guichon and M.~Guidal, Phys.Rev.Lett.{\bf 80} 5064 (1998), 
Phys.Rev. D {\bf 60}, 094017 (1999);
K.~Goeke, M.V.~Polyakov and M.~Vanderhaeghen, Prog.Part. Nucl. Phys. {\bf 47}, 401 (2001);
M.~Guidal, M.V.~Polyakov, A.V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
